---
title: "Mobile Phones"
output: flexdashboard::flex_dashboard
runtime: shiny
---


```{r setup, include=FALSE}

#install.packages("flexdashboard")
library(flexdashboard)
library(shiny)
library(rmarkdown)
library(knitr)
library(Hmisc)
library(DT)
library(data.table)
assignInNamespace("cedta.override", c(data.table:::cedta.override,"rmarkdown"), "data.table")
opts_chunk$set(echo = FALSE, comment="", warning = FALSE, message = FALSE, tidy.opts=list(width.cutoff=55), tidy = TRUE)

```

```{r source_functions}
source("Constants.R")
source("Functions.R")
```


```{r constants}
# Most constants have been placed in the file constants.R to unify the work across reporting and applications.

# Additional constants that are unique to this reporting engine can be added here.



```


```{r functions}
# Most functions have been placed in the file functions.R to unify the work across reporting and applications.
percentage.table =function(x, digits = 1){
  tab = table(x)
  percentage.tab = 100*tab/(sum(tab))
  rounded.tab = round(x = percentage.tab, digits = digits)
  return(rounded.tab)
}
# Additional functions that are unique to this reporting engine can be added here.
```

```{r read_data}
dat = fread("/Users/Chrystalla/Documents/University/Columbia/Semester 3/Data Science Consulting/Individual Project 3/Final Deliverables/mobile phone survey data.csv", verbose = F)

breaks = c(18,35,50,65,400)
labels = c("18-34", "35-49", "50-64", "65+")

dat[, AgeGroups := cut(Age, breaks = breaks, right = FALSE, labels = labels),]

breaks1 = c(0,50000,75000,100000,150000,1000000000)
labels1 = c("under 50K", "50K-75K", "75K-100K","100K-150K", "150K+")

dat[, IncomeGroup := cut(Income, breaks = breaks1, right = FALSE, labels = labels1),]

brand.traits <- names(dat)[grep(pattern = brand.pattern, x = names(dat))]

names.products <- dat[, unique(Product)]
inputs.name = c(respondent.variables, brand.traits)

```

``` {r variables}
unique.age.groups <- dat[, sort(unique(AgeGroup))]
unique.genders <- dat[, sort(unique(Gender))]
unique.income.groups <- dat[, sort(unique(IncomeGroup))]
unique.regions <- dat[, sort(unique(Region))]
unique.personas <- dat[, sort(unique(Persona))]

unique.products <- dat[, unique(Product)]
colstoavg <- names(dat)[9:20]


```


Introduction
=====================================  

This dashbaord analyzes data from a large communications company based on a marketing survey of its products' awareness and consumer perceptions. 

The survey was answered by `r dat[,length(unique(id))]` respondents, about `r dat[,length(unique(Product))]` different products. Navigate through the menubar tabs to see the reports. 

Respondents (Q1)
===================================


Row {data-height=500}
-------------------------------------

```{r q1_input}

inputPanel(selectInput(inputId = "respondent_variable", 
    label = "Select Variable:", choices = respondent.variables, 
    selected = respondent.variables[1]), checkboxInput(inputId = "respondent_show_percentages", 
    label = "Show Percentages", value = TRUE))

```


```{r q1_output}

renderPlot({
  tab <- percentage.table(x = dat[Product == Product[1], get(input$respondent_variable)])
  barplot(height = tab, space=0.01, las = 1, main = input$respondent_variable, ylab = "Percentage", xlab = input$respondent_variable, ylim = c(0, 1.2*max(tab, na.rm = TRUE)), col = rainbow(20), cex.names = 0.8 )
  
  if(input$respondent_show_percentages == TRUE){
    space_val = 0
    text(x = -0.4 + 1:length(tab) * (1+space_val), y = tab, labels = sprintf("%.1f%%", tab), pos = 3)
  }
})



```

Products (Q2)
=====================================  


Row {data-height=500}
-------------------------------------

```{r q2_input}

inputPanel(selectInput(inputId = "engagement_state", label = "Select state of Engagement:", choices = engagement.state, selected = engagement.state[1]),
           selectInput(inputId = "e_age", label = "Select Age Group:", choices = Levels.AgeGroup, selected = Levels.AgeGroup[1], multiple = TRUE),
          selectInput(inputId = "e_gender", label = "Select Gender:", choices = Levels.Gender, selected = Levels.Gender[1], multiple = TRUE),
          selectInput(inputId = "e_incomegroup", label = "Select Income Group:", choices = Levels.IncomeGroup, selected = Levels.IncomeGroup[1], multiple = TRUE),
          selectInput(inputId = "e_region", label = "Select Region:", choices = Levels.Region, selected = Levels.Region[1], multiple = TRUE),
          selectInput(inputId = "e_persona", label = "Select Persona:", choices = Levels.Persona, selected = Levels.Persona[1], multiple = TRUE),
          numericInput(inputId = "number_products", label = "Select number of products:", min = 1, max = 20, value = 1, step = 1),
          checkboxInput(inputId = "seg_show_percentages", label = "Show Percentages", value = TRUE)
           )



           #checkboxGroupInput(inputId = "sub_variable", label = "Select categories:", choices = category.variables, selected = category.variables[1]),
           #checkboxInput(inputId = "sorting_variables", label = "Sorted", value=TRUE),


```


```{r q2_output}
renderPlot({
  
  subdat = dat[get(AgeGroup) %in% input$e_age & Gender %in% input$e_gender & IncomeGroup %in% input$e_incomegroup & Region %in% input$e_region &
                 Persona %in% input$e_persona]
  tab = subdat[, .(Rate = 100*mean(get(input$engagement_state), na.rm = TRUE)/max(get(input$engagement_state), na.rm = TRUE)) , by = Product]

  setorderv(x = tab, cols = "Rate", order = -1)
  tab = tab[1:input$number_products,]
barplot(height = tab[, Rate], space = 0.01, las = 1, main = input$engagement_state, ylab = sprintf("Rate of %s", input$engagement_state), names.arg = tab[,Product], ylim = c(0, 120), xlab = "Products", axes = F, col = rainbow(20))
axis(side = 2, at = 20*(0:5), las = 2)
if(input$seg_show_percentages == TRUE){
    space_val = 0
    text(x = -0.5 + 1:length(tab) * (1+space_val), y = tab[, Rate], labels = sprintf("%.1f%%", tab[,Rate]), pos = 3)
  }
})




```


Brand Perceptions (Q3)
=====================================  

Row {data-height=500}
-------------------------------------

```{r q3_input}

inputPanel(
  selectInput(inputId = "e_age1", label = "Select Age Group:", choices = Levels.AgeGroup, selected = Levels.AgeGroup[1], multiple = TRUE),
  selectInput(inputId = "e_gender1", label = "Select Gender:", choices = Levels.Gender, selected = Levels.Gender[1], multiple = TRUE),
  selectInput(inputId = "e_incomegroup1", label = "Select Income Group:", choices = Levels.IncomeGroup, selected = Levels.IncomeGroup[1], multiple = TRUE),
  selectInput(inputId = "e_region1", label = "Select Region:", choices = Levels.Region, selected = Levels.Region[1], multiple = TRUE),
  selectInput(inputId = "e_persona1", label = "Select Persona:", choices = Levels.Persona, selected = Levels.Persona[1], multiple = TRUE),
   numericInput(inputId = "number_products1", label = "Select number of products:", min = 1, max = 20, value = 1, step = 1),
  checkboxInput(inputId = "brand_show_percentages", label = "Show Percentages", value = TRUE)
)

```



```{r q3_output}
renderPlot({
  
  
  subdat = dat[get(AgeGroup) %in% input$e_age1 & Gender %in% input$e_gender1 & IncomeGroup %in% input$e_incomegroup1 & Region %in% input$e_region1 &
                 Persona %in% input$e_persona1]
    avg.perception = subdat[,lapply(x = .SD, FUN = "mean", na.rm = TRUE), .SDcols = brand.traits, by = Product]

  avg.perception$BP_Boring_0_10 = 10 - avg.perception$BP_Boring_0_10
  avg.perception$BP_Bulky_0_10 = 10 - avg.perception$BP_Bulky_0_10
  avg.perception$BP_Fragile_0_10 = 10 - avg.perception$BP_Fragile_0_10
  avg.perception$BP_Expensive_0_10 = 10 - avg.perception$BP_Expensive_0_10
  

avg.perception[, "Average_Perception" := lapply(.SD,mean,na.rm=TRUE),by=Product, .SDcols=brand.traits]

setorderv(x = avg.perception, cols = 'Average_Perception' , order = -1)
avg.perception = avg.perception[1:input$number_products1,]


barplot(height = avg.perception[, Average_Perception], space = 0.01, las = 1, main = "Average Brand Perception", ylim = c(0, 1.2* max(avg.perception[, Average_Perception], na.rm = TRUE)), ylab = "Average Perception", names.arg = avg.perception[, Product], xlab = "Products", axes = F, col = rainbow(20))
axis(side = 2, las = 2)

  if(input$brand_show_percentages == TRUE){
    space_val = 0
    text(x = -0.5 + 1:avg.perception[, Average_Perception] * (1+space_val), y = avg.perception[, Average_Perception], labels = sprintf("%.1f%%", avg.perception[, Average_Perception]), pos = 3)
  }
})



```


Gaps in Outcomes (Q4)
=====================================  

Row {data-height=500}
-------------------------------------

```{r q4_input}

inputPanel(
  selectInput(inputId = "first_outcome_var", label = "Select first variable:", choices = engagement.state, selected = engagement.state[1]),
  selectInput(inputId = "second_outcome_var", label = "Select second variable:", choices = engagement.state, selected = engagement.state[2]),
  numericInput(inputId = "number_products3", label = "Select number of products:", min = 1, max = 20, value = 8, step = 1),
  sliderInput(inputId = "slider.digits", label = "Digits", min = 1, max = 3, value = 1, step = 1),
  checkboxInput(inputId = "gap_show_percentages", label = "Show Percentages", value = TRUE)
  
  
)

```



```{r q4_output}

renderPlot({
  
Differences = dat[, .(avg1 = mean(get(input$first_outcome_var), na.rm = TRUE), avg2 = mean(get(input$second_outcome_var), na.rm = TRUE)),by = Product]
Differences[, Difference := (100*(avg1 - avg2))]

setorderv(x = Differences, cols = "Difference", order = -1)

Differences = Differences[1:input$number_products3,]
Differences = Differences[, lapply(X = .SD, FUN= "round.numerics", digits = input$slider.digits)]



barplot(height = Differences[,Difference], space = 0.02,  las=1, col=rainbow(20), names.arg = Differences[, Product], cex.names=.7, ylab = "Difference", main = "Engagement Differences", xlab = "Product", ylim = c(0, 1.2* max(Differences[, Difference], na.rm = TRUE)))
  
axis(side = 2, las = 2)


  if(input$gap_show_percentages == TRUE){
    space_val = 0
    text(x = -0.4 + 1:Differences[,.N] * (1+space_val), y = Differences[, Difference], labels = sprintf("%.1f%%", Differences[, Difference]), pos = 3)

}
  

})



```

Models (Q5)
=====================================  

Row {data-height=500}
-------------------------------------


```{r q5_input}

inputPanel(selectInput(inputId = "engagement_state", label = "Select State of Engagement:", choices = engagement.state, selected = engagement.state[1]),
           selectInput(inputId = "unique.products", label = "Product", choices = names.products, selected = names.products[1], multiple = TRUE),
           selectInput(inputId = "input_vars", label = "Select Variables", choices = inputs.name, selected = inputs.name, multiple = TRUE),
           selectInput(inputId = "e_age2", label = "Select Age Group:", choices = Levels.AgeGroup, selected = Levels.AgeGroup[1], multiple = TRUE),
  selectInput(inputId = "e_gender2", label = "Select Gender:", choices = Levels.Gender, selected = Levels.Gender[1], multiple = TRUE),
  selectInput(inputId = "e_incomegroup2", label = "Select Income Group:", choices = Levels.IncomeGroup, selected = Levels.IncomeGroup[1], multiple = TRUE),
  selectInput(inputId = "e_region2", label = "Select Region:", choices = Levels.Region, selected = Levels.Region[1], multiple = TRUE),
  selectInput(inputId = "e_persona2", label = "Select Persona:", choices = Levels.Persona, selected = Levels.Persona[1], multiple = TRUE)
           
           
)


engagement_state = engagement.state[1]

```


```{r q5_output}


renderDataTable({
  reg_model = dat[Product %in% input$unique.products & get(AgeGroup) %in% input$e_age2 & Gender %in% input$e_gender2 & IncomeGroup %in% input$e_incomegroup2 & Region %in% input$e_region2 & Persona %in% input$e_persona2]
  
  if(input$engagement_state == Satisfaction){
    model.type = "linear"
  }
   if(input$engagement_state != Satisfaction){
    model.type = "logistic"
  
   }
  
  regression = fit.model(dt = reg_model, outcome.name = input$engagement_state, input.names = input$engagement_state,
                         model.type = model.type)
  
  datatable(data = regression)
})







```

